Adopting agile in the large: motivations, success factors and challenges

### 2014-05-08 journal/article.tex
Multisite problems

>>>>

Further problems were encountered when scaling up agile over many sites.
Operating in a distributed environment makes communication more difficult, which
causes problems with agile when frequent and effective communication needs to be
achieved. Distribution had negative effects, such as missing kick-off meetings,
reduced feeling of proximity when telecommunication is necessary, and difficulty
in arranging frequent meetings due to time zone differences [P45].
Agile project management was also problematic in a distributed setting. In a
waterfall model separate parts of projects could be isolated to different sites,
but the agile model does not allow such strict slicing of projects [P29].
In one case it was simply admitted that a distributed organization will impose
additional burden on communication and require additional care in the process,
but distribution and agile would still be used together [P48].
